Triptych

### 2020-08-27 slides/main.tex
Add presentation slides

\documentclass[aspectratio=169]{beamer}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usepackage{amsmath,amssymb}

\setbeamertemplate{footline}[frame number]
\setbeamertemplate{navigation symbols}{}

\setbeamercolor{palette primary}{fg=black,bg=white}
\setbeamercolor{palette secondary}{fg=black,bg=white}
\setbeamercolor{structure}{fg=black,bg=white}

% title frame
\defbeamertemplate*{title page}{mytheme}[1][]
{
  \begin{tikzpicture}[remember picture,overlay]
  \filldraw[white]
    (current page.north west) --
    (current page.north east) --
    ([xshift=0cm,yshift=-2cm]current page.north east)  --
    ([xshift=0cm,yshift=-2cm]current page.north west) -- cycle
    ;

  \node[opacity=0.2] at ([xshift=-1.5cm,yshift=-1cm]current page.north east) {\includegraphics[width=15cm]{monkon}};

  \node[text=black,anchor=south west,font=\sffamily\LARGE,text width=.8\paperwidth] at ([xshift=-100pt,yshift=-1cm]current page.center)(title){\raggedright\inserttitle};

  \node[text=black,anchor=south west,font=\sffamily\small,text width=.6\paperwidth] at ([xshift=-100pt,yshift=-1.5cm]current page.center)(institute){\raggedright\insertinstitute};

  \node[text=black,font=\large\sffamily,anchor=south west] at ([xshift=30pt,yshift=0.5cm]current page.south west)(date){\insertdate};

  \node[text=black,font=\large\sffamily,anchor=south west] at ([yshift=5pt]date.north west)(author){\insertauthor};
  \end{tikzpicture}
}

% definition of the symbols used in itemize
\newcommand\mysymbol{%
  \begin{tikzpicture}[xscale=0.85]
\draw[black, thick]  circle (1.5 pt);             
  \end{tikzpicture}%
  }

% definition of the itemize templates
\defbeamertemplate*{itemize item}{mysymbol}{\small\raise0.5pt\hbox{\mysymbol}}
\defbeamertemplate*{itemize subitem}{mysymbol}{\footnotesize\raise0.5pt\hbox{\mysymbol}}
\defbeamertemplate*{itemize subsubitem}{mysymbol}{\footnotesize\raise0.5pt\hbox{\mysymbol}}

\title[Transaction efficiency then and now]{Transaction efficiency then and now}
\author{Sarang Noether, Ph.D.}
\date{23 June 2019}

\institute{Monero Konferenco}

\begin{document}

\begin{frame}[plain]
\maketitle
\end{frame}

\begin{frame}
\frametitle{Disclaimer}
\begin{columns}
\begin{column}{0.2\textwidth}
\includegraphics[width=0.9\textwidth]{monero.png}
\end{column}
\begin{column}{0.8\textwidth}
The views expressed in this presentation are solely those of the author, and do not necessarily reflect those of any other person, organization, or community. \\~\\

The author receives funding support from the Monero community.
\end{column}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{What is transaction efficiency?}
\begin{columns}

\begin{column}{0.3\textwidth}
\centering
\includegraphics[width=0.4\textwidth]{icon-space.png} \\~\\
\textbf{Space} \\
Bandwidth/storage
\end{column}

\begin{column}{0.3\textwidth}
\centering
\includegraphics[width=0.4\textwidth]{icon-hourglass.png} \\~\\
\textbf{Generation time} \\
Low-capacity devices
\end{column}

\begin{column}{0.3\textwidth}
\centering
\includegraphics[width=0.4\textwidth]{icon-stopwatch.png} \\~\\
\textbf{Verification time} \\
Chain sync
\end{column}

\end{columns}
\end{frame}

\begin{frame}{Levels of optimization}
\begin{columns}
\begin{column}{0.5\textwidth}
We can optimize at difference levels:
\begin{itemize}
\item low-level cryptographic operations
\item higher-level constructions
\item protocol parameters \\~\\
\end{itemize}

We will focus on \textit{constructions} today, but all of these have effects.
\end{column}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=0.9\textwidth]{chain-growth.pdf} \\
Chain growth over time
\end{column}
\end{columns}
\end{frame}

\begin{frame}
\begin{figure}
\begin{tikzpicture}[square/.style={regular polygon,regular polygon sides=4}]
\node [square,draw,fill=lightgray] (sig) {\begin{tabular}{c}Ring \\ signature\end{tabular}};
\node [ellipse,draw,left=60pt,at=(sig.west),above=20pt] (inputs) {Input keys};
\node [ellipse,draw,left=60pt,at=(sig.west),below=20pt] (offsets) {\begin{tabular}{c}Commitment \\ offsets\end{tabular}};
\node [rectangle,draw,right=20pt,at=(sig.east)] (image) {Key image};

\draw [->] (inputs) -- (sig);
\draw [->] (offsets) -- (sig);
\draw [->] (sig) -- (image);
\end{tikzpicture}
\end{figure}
\centering
The ring signature proves key ownership, helps demonstrate transaction balance, and asserts correct key image construction.
\end{frame}

\begin{frame}
\begin{figure}
\begin{tikzpicture}[square/.style={regular polygon,regular polygon sides=4}]
\node [circle,draw] (data) {\begin{tabular}{c}Output data \\ \hline Amount ($v$)\\ Mask ($r$)\end{tabular}};
\node [rectangle,draw,left=20pt,at=(data.west),fill=lightgray] (enc) {\begin{tabular}{c}Recipient data \\ \hline $\operatorname{Enc}(v)$ \\ $\operatorname{Enc}(r)$\end{tabular}};
\node [rectangle,draw,right=20pt,at=(data.east)] (commit) {$\operatorname{Commit}(v,r)$};
\node [rectangle,draw,below=20pt,at=(commit.south),fill=lightgray] (range) {\begin{tabular}{c}Range proof \\ $v \in [0,2^n)$\end{tabular}};

\draw [->] (data) -- (enc);
\draw [->] (data) -- (commit);
\draw [->] (commit) -- (range);
\end{tikzpicture}
\end{figure}
\centering
The output constructions communicate output data to the recipient, are used (with auxiliary commitments) to show balance, and prevent amount overflow.
\end{frame}

\begin{frame}{Construction: ring signature}
We use \textbf{MLSAG} signatures to prove ownership of spent outputs without revealing the specific output in question. This type of ring signature shows more, though.
\begin{itemize}
\item The signer controls one output among a given set
\item The key image (used to detect double-spend attempts) was generated correctly
\item The (hidden) transaction amounts balance \\~\\
\end{itemize}

These signatures scale \textit{linearly} with the ring size in space, signing time, and verify time.
\end{frame}

\begin{frame}{CLSAG: the new hotness}
We propose \textbf{CLSAG} signatures to do the same thing, but more efficiently. \\~\\

CLSAG signatures use a linear combination of output signing keys and commitment keys to provide a drop-in replacement to MLSAG signatures. \\~\\

They still scale linearly, but take up less space and are faster to sign and verify. \\~\\

Security is more formally proven.
\end{frame}

\begin{frame}{Signature size (11-ring)}
\centering
\includegraphics[width=0.7\textwidth]{sig-size.pdf}
\end{frame}

\begin{frame}{Timing (11-ring)}
\begin{columns}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{sig-sign.pdf} \\~\\
\textbf{Signing}
\end{column}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{sig-verify.pdf} \\~\\
\textbf{Verification}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{Construction: commitments}
All amounts are represented as Pedersen commitments with globally fixed base:
$$\operatorname{Commit}(v,r) \equiv \underbrace{vH}_{\text{value}} + \underbrace{rG}_{\text{mask}}$$

The recipient needs to know both $v$ and $r$ to reconstruct the commitment and later use it in a ring signature to spend the output. \\~\\

Previously, both values were encrypted using the transaction shared secret $\operatorname{H}(aR,i)$:
\begin{eqnarray*}
\operatorname{Enc}(v) &\equiv& v + \operatorname{H}(\operatorname{H}(\operatorname{H}(aR,i))) \\
\operatorname{Enc}(r) &\equiv& r + \operatorname{H}(\operatorname{H}(aR,i))
\end{eqnarray*}
\end{frame}

\begin{frame}{New hotness: being clever}
\textbf{This is wasteful}. If generated randomly, both $r$ and $\operatorname{Enc}(r)$ are uniformly distributed and known only to the sender and recipient. So why include $\operatorname{Enc}(r)$ in the transaction at all? \\~\\

\textbf{Solution}: Do not include $\operatorname{Enc}(r)$. The sender and recipient both compute $$r \equiv \operatorname{H}(``\text{commitment\_mask}",\operatorname{H}(aR,i))$$ instead, and save $32$ bytes per output. \\~\\
\end{frame}

\begin{frame}{New hotness: being clever}
\textbf{This is still wasteful}. The amount cannot be larger than $8$ bytes, but is represented as a $32$-byte scalar. \\~\\

\textbf{Solution}: Restrict the amount representation to $8$ bytes and encrypt with a length-restricted XOR operation to save $24$ bytes per output:

$$\operatorname{Enc}(v) \equiv \Big( v \oplus \operatorname{H}(``\text{amount}",\operatorname{H}(aR,i)) \Big)_{0-7}$$

The full 32-byte scalar can be recovered in the same way.
\end{frame}

\begin{frame}{Commitment data size}
\centering
\includegraphics[width=0.7\textwidth]{commit.pdf}
\end{frame}

\begin{frame}{Construction: range proofs}
Since amounts are represented as commitments and balance is proven using commitment sums and differences, amounts must be restricted (relative to scalar field size) to avoid overflow. \\~\\

We must show that for $\operatorname{Commit}(v,r)$, the value $v$ is in the range $[0,2^{64})$. \\~\\

\textbf{Strategy}: Show that $v$ can be decomposed to $64$ bits, each of which is $0$ or $1$, without revealing the value of the bits. \\~\\

\textbf{Example}: $13_{10} = 1101_2 = (1 \times 2^3) + (1 \times 2^2) + (0 \times 2^1) + (1 \times 2^0)$
\end{frame}

\begin{frame}{Old way: bitwise ring signatures}
The previous method, bitwise Borromean range proofs, used ring signatures.
\begin{itemize}
\item Construct $64$ commitments, each to a bit of $v$, with masks that sum appropriately.
\item Build a ring signature over each bit commitment to show the value is either $0$ or $1$. \\~\\
\end{itemize}

To verify:
\begin{itemize}
\item Take a weighted sum of the bit commitments (using powers of $2$) and show it recovers the full amount commitment.
\item Verify the ring signature to assert that each commitment is to $0$ or $1$. \\~\\
\end{itemize}

This scales in space and time linearly with the number of bits!
\end{frame}

\begin{frame}{Bulletproofs: the new hotness}
Bulletproofs take a different approach.
\begin{itemize}
\item Reduce the range assertion to a set of vector inner product equations.
\item Prove knowledge of vector components in zero knowledge.
\item Compress this proof using a clever folding technique. \\~\\
\end{itemize}

This achieves precisely the same goal as bitwise Borromean proofs, but scales logarithmically with the number of bits. Plus:
\begin{itemize}
\item A prover can include multiple values in the same proof, to extend the logarithmic space scaling.
\item Generation and verification are still linear in the bit length, but we can use tricks.
\item Verification of a set of proofs adds only marginal time cost! (This is \textit{batching}.)
\end{itemize}
\end{frame}

\begin{frame}{2-output verification}
\centering
\includegraphics[width=0.7\textwidth]{bp-2.pdf}
\end{frame}

\begin{frame}{16-output verification}
\centering
\includegraphics[width=0.7\textwidth]{bp-16.pdf}
\end{frame}

\begin{frame}{2-output 128-batch verification}
\centering
\includegraphics[width=0.7\textwidth]{bp-2-batch-128.pdf}
\end{frame}

\begin{frame}{Proof size}
\centering
\includegraphics[width=0.7\textwidth]{bp-size.pdf}
\end{frame}

\begin{frame}{Typical transaction}
\begin{columns}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{txn-size-2-2.pdf} \\~\\
\textbf{Transaction size}
\end{column}
\begin{column}{0.5\textwidth}
\centering
\includegraphics[width=\textwidth]{txn-time-2-2.pdf} \\~\\
\textbf{Verification time}
\end{column}
\end{columns}
\begin{center}
We save $85\%$ on space and up to $81\%$ on verification time!
\end{center}
\end{frame}

\begin{frame}
\begin{center}
\textbf{These are not complete scaling solutions!}
\end{center}

These are incremental (but useful) improvements to slow blockchain growth and speed up new node sync time. \\~\\

\begin{itemize}
\item Sublinear fixed-decoy transaction protocols
\begin{itemize}
\item Lelantus
\item Omniring
\end{itemize}
\item Efficient full-anonymity transaction protocols
\begin{itemize}
\item Bulletproofs (poor verification scaling for circuits)
\item Older-style SNARKs (toxic; excellent space/time scaling)
\item Newer-style SNARKs (nontoxic; better scaling, but not quite there)
\end{itemize}
\item Off-chain transaction layers (requires new plumbing)
\begin{itemize}
\item Atomic swaps
\item Payment channels/networks
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Thank you!}
\textbf{GitHub}: \texttt{https://github.com/SarangNoether}
\begin{itemize}
\item \texttt{research-lab}: older research
\item \texttt{skunkworks}: newer research (work in branches) \\~\\
\end{itemize}

\textbf{GitLab}: \texttt{https://repo.getmonero.org/SarangNoether}
\end{frame}

>>>>

\documentclass[aspectratio=169]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{xcolor,colortbl}
\usepackage{graphics}

\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta}

\usecolortheme{wolverine}
\definecolor{monerorange}{RGB}{255, 102, 0}
\definecolor{otherorange}{RGB}{253, 188, 148}
\definecolor{redd}{RGB}{253, 150, 179}
\definecolor{grenn}{RGB}{150, 253, 189}
\definecolor{yello}{RGB}{248, 253, 150}
\setbeamercolor*{palette primary}{bg=otherorange}
\setbeamercolor*{frametitle}{bg=otherorange}
\setbeamercolor*{itemize item}{fg=monerorange}
\setbeamercolor*{itemize subitem}{fg=monerorange}
\setbeamertemplate{footline}[frame number]

\newcommand{\com}{\operatorname{Com}}

\title{Triptych}
\subtitle{Logarithmic-sized linkable ring signatures with applications}
\author{Sarang Noether, Ph.D.}
\institute{Monero Research Lab}
\date{17 September 2020}
\begin{document}

\frame{\titlepage}

\begin{frame}{Goal}
We want to build a \textbf{confidential transaction} construction with the following properties:
\begin{itemize}
\item Trust-free setup and parameters
\item Sublinear size scaling with anonymity set
\item Batchable $O(n/\log(n))$ verification
\item Safely compatible with one-time addressing
\item Supports multisignature operations
\end{itemize}
~\\
Our construction is \textbf{Triptych}.
\\~\\
This is joint work with \textbf{Brandon Goodell}.
\end{frame}

\begin{frame}{Our strategy}
\begin{center}
\begin{tikzpicture}[> = {Straight Barb[angle=60:4pt 6]}]
\node (general) {\underline{General structure}};
\node (rs) [draw, below=10pt of general] {Ring signature};
\node (lrs) [draw, below=of rs] {Linkable ring signature};
\node (2lrs) [draw, below=of lrs] {2-linkable ring signature};

\node (monero) [right=50pt of general] {\underline{Monero protocol}};
\node (schnorr) [below=10pt of monero] {Schnorr-type SAG};
\node (lsag) [below=of schnorr] {LSAG};
\node (clsag) [below=of lsag] {CLSAG/MLSAG};
\node (ringct) [draw, below=of clsag, align=center] {\textbf{Ring confidential} \\ \textbf{transaction protocol}};

\node (this) [right=60pt of monero] {\underline{\textbf{This work}}};
\node (gkb) [below=10pt of this] {\textbf{Groth/Kohlweiss/Bootle}};
\node (triptych) [below=of gkb] {\textbf{Triptych}};
\node (2triptych) [below=of triptych] {\textbf{2-Triptych}};

\draw[->] (rs) to (lrs);
\draw[->] (lrs) to (2lrs);
\draw[->] (2lrs) to (ringct);

\draw[->,dashed] (schnorr) to (lsag);
\draw[->,dashed] (lsag) to (clsag);
\draw[->,dashed] (clsag) to (ringct);

\draw[->,dashed] (gkb) to (triptych);
\draw[->,dashed] (triptych) to (2triptych);
\draw[->,dashed] (2triptych) to (ringct);
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{Ring signatures}
A \textbf{ring signature} is a signature construction that signs a message on behalf of a \underline{non-interactive} anonymity set of public keys. The signer knows the secret key to (at least) one of the public keys in the set.
\\~\\
The verifier learns only that one key in the public key set is the signer, but not which one. So
$$\operatorname{Sign}(m,\{M_0,M_1,\ldots\};(l,r)) \to \sigma$$
signs message $m$ such that $M_l$ has $r$ as its secret key, and
$$\operatorname{Verify}(m,\{M_0,M_1,\ldots\},\sigma) \to \{0,1\}$$
verifies.
\end{frame}

\begin{frame}{Ring signatures}
\begin{center}
\begin{tikzpicture}[
    box/.style = {draw, minimum width=30pt, minimum height=20pt, rounded corners, align=center},
    dot/.style = {draw, minimum width=30pt, minimum height=20pt, dashed, rounded corners, align=center},
    > = {Straight Barb[angle=60:4pt 6]}
]
\node (rs) [draw, minimum width=100pt, minimum height=40pt] {Ring signature};
\node (M1) [dot, left=of rs] {$M_1$};
\node (M0) [box, above=of M1] {$M_0$};
\node (M2) [box, below=of M1] {$M_2$};
\node (msg) [box, below=of rs] {message};
\node (sig) [box, right=of rs] {$\sigma$};

\draw[-] (M0) to (M1);
\draw[-] (M1) to (M2);
\draw[->] (M1) to (rs);
\draw[->] (msg) to (rs);
\draw[->] (rs) to (sig);
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{Groth/Kohlweiss/Bootle (GKB) ring signatures}
A paper (IACR 2014/764) by \textbf{Groth} and \textbf{Kohlweiss} uses a novel zero-knowledge proving system to build a ring signature construction; it was made more efficient (IACR 2015/643) by \textbf{Bootle} and collaborators.
\\~\\
It builds a sigma protocol for the relation
$$\Big\{\{M_0,\ldots,M_{N-1}\};(l,r) : 0 \leq l < N, M_l = \com(0,r)\Big\}$$
for commitment scheme $\com$, logarithmic in size with $N$.
\\~\\
To transform into a ring signature scheme, use the Fiat-Shamir heuristic and embed the message into the transcript hash.
\end{frame}

\begin{frame}{Properties}
Informally, we want several useful properties. These follow nicely from properties of the underlying sigma protocol.
\\~\\
\begin{itemize}
\item \textbf{Correctness}. Honest signatures always verify.
\begin{itemize}
\item Completeness
\end{itemize}
\item \textbf{Anonymity}. It is not feasible to determine the signing index.
\begin{itemize}
\item Zero knowledge
\end{itemize}
\item \textbf{Unforgeability}. It is not feasible to generate a signature without secret key knowledge.
\begin{itemize}
\item (Special) soundness
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Linkable ring signatures}
What if we wish to identify duplicate signing in a safe way?
\\~\\
A \textbf{linkable ring signature} is a ring signature that adds \underline{linkability} to the signature. Any two valid signatures that link were generated using the same (unknown) secret key. So
$$\operatorname{Link}(\sigma,\sigma') \to \{0,1\}$$
identifies whether two signatures were signed by the same key.
\\~\\
The selection of the anonymity sets can be extremely important for practical security.
\\~\\
It is possible to build constructions that are either dependent or independent of the anonymity set.
\end{frame}

\begin{frame}{Triptych linkable ring signature}
We introduce (IACR 2020/018) \textbf{Triptych} by adding linkability to the GKB construction.
\\~\\
It builds a sigma protocol for the relation
$$\Big\{\{M_0,\ldots,M_{N-1}\}, J;(l,r) : 0 \leq l < N, M_l = \com(0,r), rJ = U\Big\}$$
for globally fixed $U$, where $J$ is the \underline{linking tag}. To check linkability, compare tags.
\\~\\
To transform into a linkable ring signature scheme, use the Fiat-Shamir heuristic and embed the message into the transcript hash.
\end{frame}

\begin{frame}{From GKB to Triptych}
How does the extension from GKB to Triptych work? Treat commitments to zero as public keys, with group generator $G$.
\\~\\
In GKB, we prove knowledge of $r$ such that some commitment is of the form $rG = M$.
\\~\\
In Triptych, we reuse some of this hidden proof data about $r$ to show that $U$ is of the form $rJ = U$. Since $U$ is globally fixed, the prover can only do this if it specifies $J \equiv (1/r)U$, which is a verifiable random function.
\\~\\
Because the sigma protocol is (special) sound and the map $r \mapsto J$ is a bijection, we obtain linkability.
\end{frame}

\begin{frame}{2-linkable ring signatures}
We now extend linkable ring signatures to show knowledge of keys in \underline{parallel lists} of public keys.
\\~\\
The signer provides two lists of public keys, and shows they know the secret key to \underline{both} public keys at the \underline{same} unknown index in both lists.
\\~\\
We will still retain linkability, but only for one of the lists (more on this soon)!
\end{frame}

\begin{frame}{2-linkable ring signatures}
\begin{center}
\begin{tikzpicture}[
    box/.style = {draw, minimum width=30pt, minimum height=20pt, rounded corners, align=center},
    dot/.style = {draw, minimum width=30pt, minimum height=20pt, dashed, rounded corners, align=center},
    > = {Straight Barb[angle=60:4pt 6]}
]
\node (rs) [draw, minimum width=100pt, minimum height=40pt, align=center] {2-linkable \\ ring signature};
\node (M1) [dot, left=of rs] {$M_1$};
\node (M0) [box, above=of M1] {$M_0$};
\node (M2) [box, below=of M1] {$M_2$};

\node (P1) [dot, left=of M1] {$P_1$};
\node (P0) [box, above=of P1] {$P_0$};
\node (P2) [box, below=of P1] {$P_2$};

\node (msg) [box, below=of rs] {message};
\node (sig) [box, right=of rs] {$\sigma$};

\draw[-] (M0) to (M1);
\draw[-] (M1) to (M2);
\draw[-] (M0) to (P0);
\draw[-] (M1) to (P1);
\draw[-] (M2) to (P2);
\draw[->] (M1) to (rs);
\draw[->] (msg) to (rs);
\draw[->] (rs) to (sig);
\end{tikzpicture}
\end{center}
\end{frame}

\begin{frame}{Triptych 2-linkable ring signature}
We modify Triptych to construct a 2-linkable ring signature; this can even be done more generally.
\\~\\
It builds a sigma protocol for the relation
\begin{multline*}
\Big\{\{M_0,\ldots,M_{N-1}\}, \{P_0,\ldots,P_{N-1}\}, J;(l,r,s) : \\
0 \leq l < N, M_l = \com(0,r), P_l = \com(0,s), rJ = U\Big\}
\end{multline*}
that now includes two public key lists.
\\~\\
While we need new proof data about the secret key $s$, we can reuse existing proof data about the index $l$.
\end{frame}

\begin{frame}{Ring confidential transaction protocol}
We wish to build a \textbf{confidential transaction} protocol that:
\begin{itemize}
\item Consumes multiple transaction outputs
\item Generates multiple transaction outputs
\item Hides output amounts
\item Hides signing indices
\item Supports in-band stealth addressing
\end{itemize}
~\\
We can do this using arbitrary 2-linkable ring signatures, like 2-Triptych or CLSAG.
\end{frame}

\begin{frame}{Ring confidential transaction protocol}
Define a Pedersen commitment $\com(v,r) \equiv vH + rG$ for group generators $G,H$.
\\~\\
We wish to generate a transaction consuming $W$ existing outputs and generating $T$ new outputs.
\\~\\
Form a single anonymity set of $N \geq W$ public keys $\{M_k\}_{k=0}^{N-1}$ such that for a secret index set $\{l_u\}_{u=0}^{W-1} \subset [0,N)$, we have $M_{l_u} = r_uG$ for all $0 \leq u < W$, where each $r_u$ is a secret key.
\end{frame}

\begin{frame}{Ring confidential transaction protocol}
Let's see an example, where $W = 3$ and $N \geq 3$ is arbitrary.

\begin{center}
\begin{tikzpicture}
\node (M0) {$M_0$};
\node (M1) [right=of M0] {$M_1$};
\node (M2) [right=of M1] {$M_2$};
\node (dots) [right=of M2] {$\cdots$};
\node (MN1) [right=of dots] {$M_{N-1}$};
\node (r0) [below=of M2] {$r_0$};
\node (r1) [below=of M0] {$r_1$};
\node (r2) [below=of MN1] {$r_2$};

\draw[-, dashed] (r0) to (M2);
\draw[-, dashed] (r1) to (M0);
\draw[-, dashed] (r2) to (MN1);
\end{tikzpicture}
\end{center}

So the secret index set is $\{l_u\}_{u=1}^{W-1} = \{2, 0, N-1\}$.
\end{frame}

\begin{frame}{Ring confidential transaction protocol}
Each of the $0 \leq u < W$ consumed outputs comes associated with a commitment to an amount $a_u$:
$$P_{l_u} \equiv \com(a_u,s_u)$$

Because the Triptych proving system assumes knowledge of commitments to zero, form an \underline{commitment offset} for each consumed output, with the same value but a uniformly random mask:
$$P'_u \equiv \com(a_u,s'_u)$$

This gives these commitments to zero:
$$P_{l_u} - P'_u = \com(a_u,s_u) - \com(a_u,s'_u) = \com(0,s_u-s'_u)$$
\end{frame}

\begin{frame}{Ring confidential transaction protocol}
Generate $0 \leq j < T$ new outputs, where each has an associated amount commitment (and range proof):
$$Q_j \equiv \com(b_j,t_j)$$
We choose, for $1 \leq j < T$, random masks $t_j$. Then we set
$$t_0 \equiv \sum_{u=0}^{W-1} s'_u - \sum_{j=1}^{T-1} t_j$$
such that, if the consumed and generated amounts balance, the verifier can perform this check:
$$\sum_{u=0}^{W-1} P'_u - \sum_{j=0}^{T-1} Q_j = 0$$
\end{frame}

\begin{frame}{Ring confidential transaction protocol}
Finally, generate a signature for each of the $0 \leq u < W$ consumed outputs, using the following 2-Triptych relation inputs:
$$\Big\{\{M_k\}_{k=0}^{N-1},\{P_k-P'_u\}_{k=0}^{N-1},(1/r_u)U; (l_u,r_u,s_u-s'_u)\Big\}$$
To verify such a transaction:
\begin{itemize}
\item Verify each of the linkable ring signatures
\item Perform a linking test among all signatures
\item Ensure the balance check succeeds
\item Verify all output range proofs
\end{itemize}
\end{frame}

\begin{frame}
\centering
\includegraphics[width=\textwidth]{protocol.jpeg}
\end{frame}

\begin{frame}{Comparison}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|r|ccccc|}
\hline
& Size & Verification & Batching & Addressing & Aggregation \\
\hline
\textbf{Triptych} & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{grenn} yes & \cellcolor{redd} no \\
Arcturus & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{grenn} yes & \cellcolor{grenn} yes \\
CLSAG & \cellcolor{redd} $O(N)$ & \cellcolor{redd} $O(N)$ & \cellcolor{redd} no & \cellcolor{grenn} yes & \cellcolor{redd} no \\
Lelantus & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{redd} no & \cellcolor{redd} no \\
Omniring & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{redd} no & \cellcolor{grenn} yes & \cellcolor{grenn} yes \\
RingCT 3.0 & \cellcolor{grenn} $O(\log N)$ & \cellcolor{yello} $O(N/\log N)$ & \cellcolor{grenn} yes & \cellcolor{grenn} yes & \cellcolor{yello} padded \\
\hline
\end{tabular}
\end{center}

\begin{center}
This chart is intentionally oversimplified.
\end{center}
\end{frame}

\begin{frame}{Conclusions}
\textbf{Triptych} is a zero-knowledge proving system that can be used to construct a linkable (and 2-linkable!) ring signature construction, which in turn can power a confidential transaction model. It:
\begin{itemize}
\item Requires no trusted setup or parameters
\item Scales logarithmically in size (with superior size for reasonable anonymity sets)
\item Scales (sub)-linearly in verification time, with batching
\item Is fully compatible with in-band stealth addressing
\item Supports multisignature operations via Paillier secret sharing
\end{itemize}
\begin{center}
~\\
\textbf{\Large Questions?}
\end{center}
\end{frame}
